Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2019-09-27 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
minor fixes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
%\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
\title{Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{itemize}
\item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
\item \textcolor{red}{We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental iterative loop until the optimal cost solution of the system is reached.}
\item Experimental results show that our proposed formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies. \textcolor{red}{Our solution is far detailed and close to the commercial reality (real PV systems) than the solution presented by simulation}.
\end{itemize}

@@

\textcolor{red}{The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution. The $MaxCost$ value is a very high value put as a limit to the loop, which never will be reached because the optimal solution will be found first. The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase}. 
In particular, the loop starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).

@@

We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}). These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil. \textcolor{red}{This project, finished in March'2019, visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers\footnote{http://star-energy.coventry.ac.uk/}}. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.

@@

received his Ph.D. degree in Computer Science in 2011 from the University of Southampton, UK. Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory. He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil. Prior to joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as software engineer at industry. His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
%\title{An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative}
\title{Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{itemize}
\item Our study marks the first application of a sound and automated formal synthesis approach, which can provide accurate results of optimal sizing of stand-alone PV systems. 
\item We propose a variant CEGIS method with striking differences of how the {\sc Synthesize} and {\sc Verify} phases work together, with the abolition of the feasible solution candidate vector and the use of an incremental, iterative loop until we reach the optimal cost solution of the system.
\item Experimental results show that our proposed formal synthesis approach qualitatively outperforms an existing state-of-the-art simulation tool used in a comparative with seven case studies. Our solution is far detailed and closer to the commercial reality (real PV systems) than the solution presented by simulation.
\end{itemize}

@@

The \textit{for}-loop on line 6 ensures the search for the lowest cost to the PV solution. The $MaxCost$ value is a very high value put as a limit to the loop, which never will be reached because the optimal solution will be found first. The formal guarantee of this statement is based on the fact that the cost is verified just after a feasible technical candidate if found on {\sc Synthesize} phase. 
In particular, the loop starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in line $22$; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}).

@@

We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} (\textit{Specification}). These case studies were defined based on real houses visited by the team of a Newton Fund project in riverside communities around the Low Black River in Amazonas - Brazil. This project finished in March 2019, where we visited and surveyed 14 riverside isolated communities, aiming to evaluate the energetic habits of the dwellers.\footnote{http://star-energy.coventry.ac.uk/} For all cases, an estimated load curve (kWh) was defined based on the electronics consumers found of each house.

@@

received his Ph.D. degree in Computer Science in 2011 from the University of Southampton, UK. Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, and leads the Systems and Software Verification laboratory. He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil. Before joining the University of Manchester, he worked as a researcher at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for four years as a software engineer in industry. His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
